### 2013-02-12 mcmc.tex
sampling approximation

...What is a sampling, heurstically?..

...What is the expectation integral in the sampling approximation?  Why is that a good idea?..

>>>>

...What is a sampling, heurstically?.. Along the way, what is a pdf?..

If there is a pdf $p(x)$ for some quantity $x$, which can be a scalar
or a multi-element vector or list or blob, we can define
\emph{expectation values} $E[x]$ for $x$ or for any quantity that can
be expressed as a function $q(x)$ of $x$:
\begin{eqnarray}
E[x] &\equiv& \int x\,p(x)\,\dd x
\\
E[q] &\equiv& \int q(x)\,p(x)\,\dd x
\quad ,
\end{eqnarray}
where the integrals are implicitly definite integrals over the domain
of $x$ (all the parts of $x$ space in which $p(x)$ is finite) and the
integrals are multi-dimensional if $x$ is multi-dimensional.  These
expectation values are the mean values of $x$ and $q(x)$ under the
pdf.  A good sampling---really the definition of a good
sampling---makes the sampling approximation to these integrals
accurate.  With a good sampling $\setofall{x_k}_{k=1}^K$ the integrals
get replaced with sums over samples $x_k$:
\begin{eqnarray}
E[x] &\approx& \frac{1}{K}\,\sum_{k=1}^K x_k
\\
E[q] &\approx& \frac{1}{K}\,\sum_{k=1}^K q(x_k)
\quad .
\end{eqnarray}
That is, a sampling is good when any expectation value of interest is
accurately computed via the sampling approximation.  Your conditions
on your sampling will depend on the expectations you want to compute,
and the accuracies you need.
